An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-06-17 poly-embed-journal/poly-embed-journal.tex
Making notation consistent and adding a few definitions

\jessie{Lemma X}
\begin{lemma}
	Let $f: \simplex \to \reals_+$ be a (concave) polyhedral function.
	There exists a unique set of loss vectors $\V$ of minimum cardinality such that $f(p) = \min_{v \in \V} \inprod{v}{p}$ for all $p\in\simplex$.
	Define $\theta(v) = \{p \in \simplex \mid \inprod{v}{p} = f(p)\}$, and $\Theta := \{\theta(v) \mid v \in \V\}$.
	Furthermore, let $L: \R \to \reals^\Y_+$ be any loss whose infimum is attained with Bayes risk $\risk L=f$ and let $\Gamma := \prop{L}$.
	Then $L$ has a finite minimum representative set, and for any minimum representative set $\R^* \subseteq \R$,
	\begin{enumerate}
		\item $\{L(r^*) \mid r^* \in \R^*\} = \V$,
		\item $\{\Gamma_r \mid r \in \R^*\} = \Theta$ is exactly the set of full-dimensional level sets of $\Gamma$\jessie{relative to $\reals^{n-1}$},
		\item For any $r \in \R$, there exists $r^* \in \R^*$ such that $\Gamma_r \subseteq \Gamma_{r^*}$\jessie{power diagrams stuff}.
	\end{enumerate}
\end{lemma}

@@

Phase 1: construct $\V$. 
\jessie{In appendix, try to flesh out phase 1.  Follow (and note) textbook(s) where definitions come from}
\jessie{Definitions coming from Ziegler Lectures on Convex Polytopes unless otherwise noted}
\jessie{Lecture notes on $H$-redundancies found in Chapter 8 here: \url{https://people.inf.ethz.ch/fukudak/lect/pclect/notes2014/PolyComp2014.pdf}}
\jessie{$\delta(x\mid C)$ is the $0-\infty$ indicator if $x \in C$.}
\jessie{Introduce general notation upfront}
\jessie{Strike a balance between things you know are true but need citations for, and having a fully fleshed out argument.  Don't block on finding the right reference.}

By Rockafellar, we have $f$ polyhedral if and only if it can be written as the max of a finite set of linear functions $\hat \V$ over $\reals^\Y_+$. 
Therefore, $f(p) = \min_{v\in\hat\V} \inprod{p}{v}$ over $p \in \reals_+^\Y$. 
We extend $f$ to $g(x) = \min_{v\in\hat\V} \inprod{x}{v}$ for $x \in \reals^\Y_+$ and $g(x) = \infty$ otherwise, and define $g(0) = 0$. 
That is, $g(x) = \min_{v \in \hat \V} \inprod{x}{v} + \delta(x \mid \reals^\Y_+)$, which is also polyhedral by Rockafellar. 
Note that $g$ and $f$ match on $\reals^\Y_+$.
Define $G = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y \times \reals$ as the hypograph of $g$.

Let $H_{v}^+ := \{ (x,c) \in \reals^\Y \times \reals \mid \inprod{x}{v} - c \geq 0\}$ as the halfspace generated by a vector $v$ and $H_{v} := \{ (x,c) \in \reals^\Y \times \reals \mid \inprod{x}{v} - c = 0\}$ and as the hyperplane defining the boundaries of this halfspace.
Abusing notation, we will say $H_y^+ := \{(x,c) \mid x_y \geq 0\}$, and $H_y := \{(x,c) \mid x_y = 0\}$ for $y \in \Y$. %\jessie{$H_y = H_{e_y}$ doesn't quite match up with what was here before; before, $H^+_y\{(x,c) \mid x_y \geq 0\}$, where this now has a $-c$ in that term.}
For any set of vectors, $Z$, let $\H_{Z} = \{H_z^+ \mid z\in Z\}$, and denote $\H = \H_{\hat \V} \cup \H_\Y$\footnote{Slightly abusing notation, we denote $\H_\Y := \{H_y \mid y \in \Y\}$} as the set of halfspaces defining $G$; $\H_{\hat V}$ defines $G$ on $\reals^\Y_+$, and $\H_\Y$ determines $G$ outside  the nonnegative orthant.
Then $G = \cap \H$, and is full-dimensional, e.g., $\dim(\affhull(G)) = n$.
Since $G$ is a full-dimensional polyhedron, it has a $H$-rep $H'$ uniquely determined by the facets of $G$ by \citep[Proposition 4.5]{gallier2008notes}.
Take $\H' := \H_{H'}$; we claim that $\H' \subseteq \H$ and $G = \cap \H'$. \jessie{$\H' \subseteq \H$ seems to follow from Proposition 8.5 from \url{https://people.inf.ethz.ch/fukudak/lect/pclect/notes2014/PolyComp2014.pdf}}
%Consider the set $\V := H' \setminus e_\Y$\footnote{$e_\Y := \{e_i\}_{i=1}^n$}. \jessie{Doesn't quite type check, hence the comment out}
We argue $\H_\Y \subseteq \H'$; if there was a $y \in \Y$ such that $H_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H'$, then we would either have some $c_1 > 0$ such that $\{(x,c) \mid x_y \geq c_1\} \in \H'$, or we have a point $x$ such that $x_y < 0$ but $g(x) < \infty$.
The first cannot happen as we take $f$ to be defined (and finite) on $\reals_+^\Y$, and $f$ and $g$ match on the domain of $f$.
Moreover, the second cannot be true by construction of $g$.
Therefore, we have $\H' \setminus \H_\Y = \H_\V$ for some $\V \subseteq \V'$.

$\V$ is precisely the set we are looking for; it is uniquely generated by $f$ since $\H'$ and $\H_\Y$ are unique, and minimum cardinality since $\H'$ has minimum cardinality \jessie{Since it has finite cardinality and uniquely determines $g$}.  
Moreover, $F_v := H_v \cap G$ is a facet of $G$ for each $v\in\V$~\citep[Proposition 4.5]{gallier2008notes}. 
%\jessie{by analog of Ziegler Theorem 2.15; more directly by Gallier notes \url{https://arxiv.org/pdf/0805.0292.pdf} Prop 4.5}

Define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
We can write any face $F_v = \{x \in \reals^\Y \mid \inprod{x}{v} = g(x)\}$.
We claim $\cup_{v \in \V}\pi(F_v) = \reals_+^\Y$.
If there was a $v \in \V$ such that $\pi(F_v) \not \subseteq \reals_+^\Y$, this would imply there is some $x \not \in \reals_+^\Y$ such that $\inprod{x}{v} = c < \infty = g(x)$, contradicting $F_v$ supporting $g$ at $x$.
Thus, $\cup_{v \in \V} \pi(F_v) \subseteq \reals_+^\Y$.
Now for the other direction of subset inclusion, observe that for all $x \in \reals^\Y_+$, we have $g(x) = f(x) = \min_{v \in \V}\inprod{v}{x}$, so there is a $v \in \V$ supporting $g$ at $x$, and therefore $x \in \pi(F_v)$ for some $v \in \V$, and is therefore in the union of projections.
As we have shown both directions of set inclusion, we must have $\cup_{v \in \V}\pi(F_v) = \reals_+^\Y$.
Note that we can also take $\theta(v) = F_v \cap \simplex$.

@@

\raf{Maybe add def supporting hyperplane; cor of face def is that nonempty face iff supporting hyperplane}

@@

@@

\subsection{Phase 1: construct $\V$}

Set up notation and define $g,G$
\begin{itemize}\setlength{\itemsep}{0pt}
\item Let $f:\reals^\Y\to\reals_+\cup\{-\infty\}$ be a polyhedral concave function with $\dom(f) = \simplex$.
\begin{claim}
	We may write $f(p) = \min_{v\in\hat\V} \inprod{p}{v}$ for some finite set $\hat\V \subseteq \reals^\Y_+$ \raf{show you can do this using the $h$ and $\delta$ representation from Rockafellar -- argue that because $p\in\simplex$ we can write $\inprod{p}{b_i}-\beta_i = \inprod{p}{b_i-\beta_i\ones}$.}
\end{claim}
\begin{proof}
  We will think of $f$ as defined $f:\reals^\Y\to\reals_+\cup\{-\infty\}$  with $\dom(f) = \simplex$.
  \raf{Make formal}
  Since $f$ is defined over the simplex, and therefore $\sum_i p_i = 1$, we can write any inner product $\inprod{p}{b} - \beta = \inprod{p}{b} - \inprod{p}{\beta \ones} = \inprod{p}{b - \beta \ones}$.
	Moreover, since $f$ is polyhedral, it is finitely generated \jessie{Rockafellar 19.1.2} and can be written 
	\begin{align*}
	f(p) &= h(p) - \delta(p \mid C)\\
		 &= \min(\inprod{p}{b_1} - \beta_1, \ldots, \inprod{p}{b_k} - \beta_k) - \delta(p \mid \simplex\jessie{?})\\
		 &= \min(\inprod{p}{b_1 - \beta_1 \ones}, \ldots, \inprod{p}{b_k - \beta_k \ones}) - \delta(p \mid \simplex)~.~
	\end{align*}
\end{proof}

\item We now extend $f$ from the simplex to the nonnegative reals.
\begin{definition}
	Define the function $g : \reals_+^\Y \to \reals_+$ by extending $-f$
	\begin{align*}
	g(x) = \min_{v\in\hat\V} \inprod{x}{v} - \delta(x \mid \reals_+^\Y)~,~
	\end{align*}
	taking $g(0) = 0$.
\end{definition}
%Extend to $g(x) = \min_{v\in\hat\V} \inprod{x}{v}$ for $x \in \reals^\Y_+$ and $g(x) = -\infty$ otherwise.  Def $g(0) = 0$.

\item Define $G = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y \times \reals$ to be the hypograph of $g$.
\end{itemize}

\begin{itemize}
\item   We define $H^+_v := H^+_{([v;-1], 0)}$ for a $v \in \reals^\Y_+$, where $[v; -1]\in\reals^\Y_+\times\reals$.
\item Additionally, denote $H_y^+ := H_{([e_y; 0], 0)}^+$. % \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$.
\item 	Again, we let $H_v := H_{([v;-1], 0)}$ for $v \in \reals^\Y_+$.

@@

%\item Let $H_y^+ := \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$.
\item Let $\H_{\hat \V} = \{H_v^+ \mid v\in\hat\V\}$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$, $\H = \H_{\hat \V} \cup \H_\Y$.
\end{itemize}

\begin{claim}
	$G = \cap \H$.
\end{claim}
\begin{proof}
	$(x,c) \in G \iff g(x) - c \geq 0 \iff \min_{v \in \hat \V}\inprod{v}{x} - c \geq 0$ and $x \in \reals_+^\Y$, which is true if and only if $\inprod{v}{x} - c \geq 0 \,\forall v \in \hat \V$ and $x_y \geq 0$ for all $y$.
	In turn, this statement holds if and only if $(x,c) \in H^+_v$ for all $v \in \hat \V$ and in $H^+_y$ for all $y \in \Y$, so $(x,c) \in \cap \H$.
\end{proof}

@@

\begin{claim}
	Claim: $G$ is $(|\Y|+1)$-dimensional.  \raf{$g$ is nonnegative on $\reals^\Y_+$, so $G$ contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is full-dim.}
\end{claim}
\begin{proof}
	Since $g$ is nonnegative on $\reals_+^\Y$, $G$ therefore contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is $(|\Y| + 1)$-dimensional.
\end{proof}

\begin{claim}
	\raf{This is the important general polyhedra result to cite/state.  Note: we'll have to work half-spaces of the form $H_{(w,\beta)}^+ = \{ z \in \reals^{n+1} \mid \inprod{z}{w} - \beta \geq 0\}$.}  
	%Since $G$ is a full-dimensional polyhedron, with a unique H-rep by [cite].
	There is some unique $\H' \subseteq \H$ such that $G = \cap \H'$. \jessie{$\H \subseteq \H$ since $G = \cap \H' = \cap \H$; something about smallest cardinality here?}
	Moreover, for each $H_{(w_i, b_i)} \in\H'$, the face $F_{(w_i, b_i)} = H_{(w_i, b_i)} \cap G$ is a facet. %\raf{make formal}
\end{claim}
  \begin{proof}
  	Since $G$ is full-dimensional, this follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
%	We know $G$ has a halfspace representation $G = G(H', \vec 0)$ uniquely determined by the facets of $G$ by \citep[Proposition 4.5]{gallier2008notes} \jessie{Another reference: Ziegler Proposition 2.15 analagous extension}.
%	Take $\H' := \H_{H'}$; we claim that $\H' \subseteq \H$ and $G = \cap \H'$. \jessie{$\H' \subseteq \H$ seems to follow from Proposition 8.5 from \url{https://people.inf.ethz.ch/fukudak/lect/pclect/notes2014/PolyComp2014.pdf}}
  \end{proof}

\begin{claim}
	$\H_\Y \subseteq \H'$.
\end{claim}
\begin{proof}
	We argue $\H_\Y \subseteq \H'$; if there was a $y \in \Y$ such that $H_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H'$, then we would either have some $c_1 > 0$ such that $\{(x,c) \mid x_y \geq c_1\} \in \H'$, or we have a point $x$ such that $x_y < 0$ but $g(x) > -\infty$.
	The first cannot happen as we take $f$ to be defined (and finite) on $p = \delta_y \in \simplex$, and $f$ and $g$ match on the domain of $f$.
	Moreover, the second cannot be true by construction of $g$.	
\end{proof}

\begin{claim}
  There is a unique finite set $\V^* \subseteq \reals^\Y_+$ such that $\H^* = \H_\Y \cup \H_{\V^*}$.
  Moreover, $F_v$ is a facet of $G$ for each $v\in\V$.
\end{claim}
\begin{proof}
\raf{Argue that all facets of $G$ are an $H_y \cap G$ or some $H_v \cap G$.  Thus, we can define $\V$ by $\H_\Y \cup \H_\V = \H^*$.  (I.e., $\H^* \setminus \H_\Y = \H_\V$ for some $\V$.)}

\raf{The moreover} follows immediately since $\H_\V \subseteq \H'$ and every $H^+ \in \H'$ defines a facet by Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
%	First, observe that by construction, $H_v = \{(x,c) \mid \inprod{v}{x} - c \geq 0\}$ is a valid inequality for $G$, and thus $F_v$ is a face of $G$ by definition.
%	To see that $F_v$ is a facet, we must show it is $\dim(G) - 1 = |\Y|$-dimensional.
%	This holds true if we can fit a $|\Y|$-dimensional ball in $F_v$.
%	If we could not fit such a ball in $F_v$, \jessie{contradict $\V$ minimum cardinality}
\end{proof}

\begin{corollary}
  Let $\V \subseteq \reals^\Y_+$ be a finite set such that $\H = \H_\Y \cup \H_\V$ satisfies $P = \cap \H$.  Then $\V^* \subseteq \V$.
\end{corollary}
\begin{proof}
  $\H_\Y \cup \H_\V = \H^* \subseteq \H = \H_\Y \cup \H_{\hat \V}$, ergo $\V \subseteq \hat \V$.
\end{proof}

\subsection{Projections to the positive orthant}
\begin{itemize}
\item Define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
\item 
\begin{claim}
	For all $x\in\reals^\Y_+$, there exists $v\in\V$ such that $H_v$ supports $G$ at $(x,g(x))$.
\end{claim}
\begin{proof}
We can write any face $F_v = H_v \cap G = \{x \in \reals_+^{d-1} \mid \inprod{x}{v} = g(x)\}$.
If there was no $v \in \V$ such that $x \in F_v$, then $g(x) = \min_{H_v \in \H_\Y} \inprod{v}{x}$.
As these halfspaces are vertical, we have $g(x) = -\infty$, which does not support $G$ at $(x, g(x))$ since $x \in \reals_+^\Y$, yielding a contradiction.
\jessie{Don't like this. Slash not true.  There's something implicit about all the normals being in $\R^d_-$ and $x \in \reals^d_+$.  Haven't proven the first claim}
%We claim $\cup_{v \in \V}\pi(F_v) = \reals_+^\Y$.
%If there was a $v \in \V$ such that $\pi(F_v) \not \subseteq \reals_+^\Y$, this would imply there is some $x \not \in \reals_+^\Y$ such that $\inprod{x}{v} = c < \infty = g(x)$, contradicting $F_v$ supporting $g$ at $x$.
%Thus, $\cup_{v \in \V} \pi(F_v) \subseteq \reals_+^\Y$.
%Now for the other direction of subset inclusion, observe that for all $x \in \reals^\Y_+$, we have $g(x) = f(x) = \min_{v \in \V}\inprod{v}{x}$, so there is a $v \in \V$ supporting $g$ at $x$, and therefore $x \in \pi(F_v)$ for some $v \in \V$, and is therefore in the union of projections.
%As we have shown both directions of set inclusion, we must have $\cup_{v \in \V}\pi(F_v) = \reals_+^\Y$.	
\end{proof}

>>>>

\jessie{Lemma X}
\begin{lemma}
	Let $f: \simplex \to \reals_+$ be a (concave) polyhedral function.
	There exists a unique set of loss vectors $\V^*$ of minimum cardinality such that $f(p) = \min_{v \in \V^*} \inprod{v}{p}$ for all $p\in\simplex$.
	Define $\theta(v) = \{p \in \simplex \mid \inprod{v}{p} = f(p)\}$, and $\Theta := \{\theta(v) \mid v \in \V^*\}$.
	Furthermore, let $L: \R \to \reals^\Y_+$ be any loss whose infimum is attained with Bayes risk $\risk L=f$ and let $\Gamma := \prop{L}$.
	Then $L$ has a finite minimum representative set, and for any minimum representative set $\R^* \subseteq \R$,
	\begin{enumerate}
		\item $\{L(r^*) \mid r^* \in \R^*\} = \V^*$,
		\item $\{\Gamma_r \mid r \in \R^*\} = \Theta$ is exactly the set of full-dimensional level sets of $\Gamma$\jessie{relative to $\reals^{n-1}$},
		\item For any $r \in \R$, there exists $r^* \in \R^*$ such that $\Gamma_r \subseteq \Gamma_{r^*}$\jessie{power diagrams stuff}.
	\end{enumerate}
\end{lemma}

@@

Phase 1: construct $\V^*$. 
\jessie{In appendix, try to flesh out phase 1.  Follow (and note) textbook(s) where definitions come from}
\jessie{Definitions coming from Ziegler Lectures on Convex Polytopes unless otherwise noted}
\jessie{Lecture notes on $H$-redundancies found in Chapter 8 here: \url{https://people.inf.ethz.ch/fukudak/lect/pclect/notes2014/PolyComp2014.pdf}}
\jessie{$\delta(x\mid C)$ is the $0-\infty$ indicator if $x \in C$.}
\jessie{Introduce general notation upfront}
\jessie{Strike a balance between things you know are true but need citations for, and having a fully fleshed out argument.  Don't block on finding the right reference.}

By Rockafellar, we have $f$ polyhedral if and only if it can be written as the max of a finite set of linear functions $\V$ over $\reals^\Y_+$. 
Therefore, $f(p) = \min_{v\in\V} \inprod{p}{v}$ over $p \in \reals_+^\Y$. 
We extend $f$ to $g(x) = \min_{v\in\V} \inprod{x}{v}$ for $x \in \reals^\Y_+$ and $g(x) = \infty$ otherwise, and define $g(0) = 0$. 
That is, $g(x) = \min_{v \in \V} \inprod{x}{v} + \delta(x \mid \reals^\Y_+)$, which is also polyhedral by Rockafellar. 
Note that $g$ and $f$ match on $\reals^\Y_+$.
Define $G = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y \times \reals$ as the hypograph of $g$.

Let $H_{v}^+ := \{ (x,c) \in \reals^\Y \times \reals \mid \inprod{x}{v} - c \geq 0\}$ as the halfspace generated by a vector $v$ and $H_{v} := \{ (x,c) \in \reals^\Y \times \reals \mid \inprod{x}{v} - c = 0\}$ and as the hyperplane defining the boundaries of this halfspace.
Abusing notation, we will say $H_y^+ := \{(x,c) \mid x_y \geq 0\}$, and $H_y := \{(x,c) \mid x_y = 0\}$ for $y \in \Y$. %\jessie{$H_y = H_{e_y}$ doesn't quite match up with what was here before; before, $H^+_y\{(x,c) \mid x_y \geq 0\}$, where this now has a $-c$ in that term.}
For any set of vectors, $Z$, let $\H_{Z} = \{H_z^+ \mid z\in Z\}$, and denote $\H = \H_{\V} \cup \H_\Y$\footnote{Slightly abusing notation, we denote $\H_\Y := \{H_y \mid y \in \Y\}$} as the set of halfspaces defining $G$; $\H_{\hat V}$ defines $G$ on $\reals^\Y_+$, and $\H_\Y$ determines $G$ outside  the nonnegative orthant.
Then $G = \cap \H$, and is full-dimensional, e.g., $\dim(\affhull(G)) = n$.
Since $G$ is a full-dimensional polyhedron, it has a $H$-rep $H'$ uniquely determined by the facets of $G$ by \citep[Proposition 4.5]{gallier2008notes}.
Take $\H' := \H_{H'}$; we claim that $\H' \subseteq \H$ and $G = \cap \H'$. \jessie{$\H' \subseteq \H$ seems to follow from Proposition 8.5 from \url{https://people.inf.ethz.ch/fukudak/lect/pclect/notes2014/PolyComp2014.pdf}}
%Consider the set $\V^* := H' \setminus e_\Y$\footnote{$e_\Y := \{e_i\}_{i=1}^n$}. \jessie{Doesn't quite type check, hence the comment out}
We argue $\H_\Y \subseteq \H'$; if there was a $y \in \Y$ such that $H_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H'$, then we would either have some $c_1 > 0$ such that $\{(x,c) \mid x_y \geq c_1\} \in \H'$, or we have a point $x$ such that $x_y < 0$ but $g(x) < \infty$.
The first cannot happen as we take $f$ to be defined (and finite) on $\reals_+^\Y$, and $f$ and $g$ match on the domain of $f$.
Moreover, the second cannot be true by construction of $g$.
Therefore, we have $\H^* \setminus \H_\Y = \H_{\V^*}$ for some $\V \subseteq \V^*$.

$\V^*$ is precisely the set we are looking for; it is uniquely generated by $f$ since $\H'$ and $\H_\Y$ are unique, and minimum cardinality since $\H'$ has minimum cardinality \jessie{Since it has finite cardinality and uniquely determines $g$}.  
Moreover, $F_v := H_v \cap G$ is a facet of $G$ for each $v\in\V^*$~\citep[Proposition 4.5]{gallier2008notes}. 
%\jessie{by analog of Ziegler Theorem 2.15; more directly by Gallier notes \url{https://arxiv.org/pdf/0805.0292.pdf} Prop 4.5}

Define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
We can write any face $F_v = \{x \in \reals^\Y \mid \inprod{x}{v} = g(x)\}$.
We claim $\cup_{v \in \V^*}\pi(F_v) = \reals_+^\Y$.
If there was a $v \in \V^*$ such that $\pi(F_v) \not \subseteq \reals_+^\Y$, this would imply there is some $x \not \in \reals_+^\Y$ such that $\inprod{x}{v} = c < \infty = g(x)$, contradicting $F_v$ supporting $g$ at $x$.
Thus, $\cup_{v \in \V^*} \pi(F_v) \subseteq \reals_+^\Y$.
Now for the other direction of subset inclusion, observe that for all $x \in \reals^\Y_+$, we have $g(x) = f(x) = \min_{v \in \V^*}\inprod{v}{x}$, so there is a $v \in \V^*$ supporting $g$ at $x$, and therefore $x \in \pi(F_v)$ for some $v \in \V^*$, and is therefore in the union of projections.
As we have shown both directions of set inclusion, we must have $\cup_{v \in \V^*}\pi(F_v) = \reals_+^\Y$.
Note that we can also take $\theta(v) = F_v \cap \simplex$.

@@

%\raf{Maybe add def supporting hyperplane; cor of face def is that nonempty face iff supporting hyperplane}
\begin{definition}[Supports]
	A hyperplane $H$ \emph{supports} the polyhedron $P$ if 
	(i) $P \subseteq H^+$ or $P \subseteq -H^+$, and
	(ii)$H \cap \mathrm{bd}(P) \neq \emptyset$.
	Moreover, $H$ supports $P$ at $x$ if $x \in H \cap \mathrm{bd}(P)$.
\end{definition}

@@

\begin{corollary}
	A face $F_{(w,b)}$ of the polyhedron $P$ such that $F_{(w,b)} = P \cap H_{(w,b)}$ is nonempty if and only if $H_{(w,b)}$ is a supporting hyperplane of $P$.
\end{corollary}

@@

\subsection{Phase 1: construct $\V^*$}

%Set up notation and define $g,G$
Let $f:\reals^\Y\to\reals_+\cup\{-\infty\}$ be a polyhedral concave function with $\dom(f) = \simplex$.
\begin{claim}
	We may write $f(p) = \min_{v\in\V} \inprod{p}{v}$ for some finite set $\V \subseteq \reals^\Y_+$ \raf{show you can do this using the $h$ and $\delta$ representation from Rockafellar -- argue that because $p\in\simplex$ we can write $\inprod{p}{b_i}-\beta_i = \inprod{p}{b_i-\beta_i\ones}$.}
\end{claim}
\begin{proof}
  We will think of $f$ as defined $f:\reals^\Y\to\reals_+\cup\{-\infty\}$  with $\dom(f) = \simplex$.
  \raf{Make formal}
  For $p \in \simplex$, we know $\sum_i p_i = 1$, and can write any inner product $\inprod{p}{b} - \beta = \inprod{p}{b} - \inprod{p}{\beta \ones} = \inprod{p}{b - \beta \ones}$.
  If $p \not \in \simplex$, then $f(p) = -\infty$ and inner products are not used to compute $F$.
  Moreover, since $f$ is polyhedral, it is finitely generated \citep[Proposition 19.1.2]{rockafellar1997convex} and can be written 
	\begin{align*}
	f(p) &= h(p) - \delta(p \mid C)\\
		 &= \min(\inprod{p}{b_1} - \beta_1, \ldots, \inprod{p}{b_k} - \beta_k) - \delta(p \mid \simplex)\\
		 &= \min(\inprod{p}{b_1 - \beta_1 \ones}, \ldots, \inprod{p}{b_k - \beta_k \ones}) - \delta(p \mid \simplex)~.~
	\end{align*}
\end{proof}

We now extend $f$ from the simplex to the nonnegative reals.
\begin{definition}
	Define the function $g : \reals_+^\Y \to \reals_+$ by extending $-f$
	\begin{align*}
	g(x) = \min_{v\in\V} \inprod{x}{v} - \delta(x \mid \reals_+^\Y)~,~
	\end{align*}
	taking $g(0) = 0$.
\end{definition}
%Extend to $g(x) = \min_{v\in\V} \inprod{x}{v}$ for $x \in \reals^\Y_+$ and $g(x) = -\infty$ otherwise.  Def $g(0) = 0$.

\begin{itemize}
\item Define $G = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y \times \reals$ to be the hypograph of $g$.
\item We define $H^+_v := H^+_{([v;-1], 0)}$ for a $v \in \reals^\Y_+$, where $[v; -1]\in\reals^\Y_+\times\reals$.
\item Additionally, denote $H_y^+ := H_{([e_y; 0], 0)}^+$. % \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$.
\item Again, we let $H_v := H_{([v;-1], 0)}$ for $v \in \reals^\Y_+$.

@@

%\item Let $H_y^+ := \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$.
\item Let $\H_{\V} = \{H_v^+ \mid v\in\V\}$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$, $\H = \H_{\V} \cup \H_\Y$.
\end{itemize}

\begin{claim}
	$G = \cap \H$.
\end{claim}
\begin{proof}
	$(x,c) \in G \iff g(x) - c \geq 0 \iff \min_{v \in \V}\inprod{v}{x} - c \geq 0$ and $x \in \reals_+^\Y$, which is true if and only if $\inprod{v}{x} - c \geq 0 \,\forall v \in \V$ and $x_y \geq 0$ for all $y$.
	In turn, this statement holds if and only if $(x,c) \in H^+_v$ for all $v \in \V$ and in $H^+_y$ for all $y \in \Y$, so $(x,c) \in \cap \H$.
\end{proof}

@@

\begin{claim}
	Claim: $G$ is $(|\Y|+1)$-dimensional.  %\raf{$g$ is nonnegative on $\reals^\Y_+$, so $G$ contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is full-dim.}
\end{claim}
\begin{proof}
	Since $g$ is nonnegative on $\reals_+^\Y$, $G$ therefore contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is $(|\Y| + 1)$-dimensional.
\end{proof}

\begin{claim}
	\raf{This is the important general polyhedra result to cite/state.  Note: we'll have to work half-spaces of the form $H_{(w,\beta)}^+ = \{ z \in \reals^{n+1} \mid \inprod{z}{w} - \beta \geq 0\}$.}  
	%Since $G$ is a full-dimensional polyhedron, with a unique H-rep by [cite].
	There is some unique $\H^* \subseteq \H$ such that $G = \cap \H^*$. 
	%\jessie{$\H^* \subseteq \H$ since $G = \cap \H^* = \cap \H$; something about smallest cardinality here?}
	Moreover, for each $H_{(w_i, b_i)} \in\H^*$, the face $F_{(w_i, b_i)} = H_{(w_i, b_i)} \cap G$ is a facet. %\raf{make formal}
\end{claim}
  \begin{proof}
  	Since $G$ is full-dimensional, this follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
%	We know $G$ has a halfspace representation $G = G(H', \vec 0)$ uniquely determined by the facets of $G$ by \citep[Proposition 4.5]{gallier2008notes} \jessie{Another reference: Ziegler Proposition 2.15 analagous extension}.
%	Take $\H' := \H_{H'}$; we claim that $\H' \subseteq \H$ and $G = \cap \H'$. \jessie{$\H' \subseteq \H$ seems to follow from Proposition 8.5 from \url{https://people.inf.ethz.ch/fukudak/lect/pclect/notes2014/PolyComp2014.pdf}}
  \end{proof}

\begin{claim}
	$\H_\Y \subseteq \H^*$.
\end{claim}
\begin{proof}
	We argue $\H_\Y \subseteq \H^*$; if there was a $y \in \Y$ such that $H_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H^*$, then we would either have some $c_1 > 0$ such that $\{(x,c) \mid x_y \geq c_1\} \in \H^*$, or we have a point $x$ such that $x_y < 0$ but $g(x) > -\infty$.
	The first cannot happen as we take $f$ to be defined (and finite) on $p = \delta_y \in \simplex$, and $f$ and $g$ match on the domain of $f$.
	Moreover, the second cannot be true by construction of $g$.	
\end{proof}

\begin{claim}
  There is a unique finite set $\V^* \subseteq \reals^\Y_+$ such that $\H^* = \H_\Y \cup \H_{\V^*}$.
  Moreover, $F_v$ is a facet of $G$ for each $v\in\V^*$.
\end{claim}
\begin{proof}
\raf{Argue that all facets of $G$ are an $H_y \cap G$ or some $H_v \cap G$.  Thus, we can define $\V^*$ by $\H_\Y \cup \H_{\V^*} = \H^*$.  (I.e., $\H^* \setminus \H_\Y = \H_{\V^*}$ for some $\V^*$.)}

The moreover follows immediately since $\H_{\V^*} \subseteq \H^*$ and every $H^+ \in \H^*$ defines a facet by Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
%	First, observe that by construction, $H_v = \{(x,c) \mid \inprod{v}{x} - c \geq 0\}$ is a valid inequality for $G$, and thus $F_v$ is a face of $G$ by definition.
%	To see that $F_v$ is a facet, we must show it is $\dim(G) - 1 = |\Y|$-dimensional.
%	This holds true if we can fit a $|\Y|$-dimensional ball in $F_v$.
%	If we could not fit such a ball in $F_v$, \jessie{contradict $\V$ minimum cardinality}
\end{proof}

\begin{corollary}
  Let $\V \subseteq \reals^\Y_+$ be a finite set such that $\H = \H_\Y \cup \H_\V$ satisfies $P = \cap \H$.  Then $\V^* \subseteq \V$.
\end{corollary}
\begin{proof}
  $\H_\Y \cup \H_{V^*} = \H^* \subseteq \H = \H_\Y \cup \H_{\V}$, ergo $\V^* \subseteq \V$.
\end{proof}

\subsection{Projections to the positive orthant}
\begin{itemize}
\item Define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
\item 
\begin{claim}
	For all $x\in\reals^\Y_+$, there exists $v\in\V^*$ such that $H_v$ supports $G$ at $(x,g(x))$.
\end{claim}
\begin{proof}
We can write any face $F_v = H_v \cap G = \{x \in \reals_+^{d-1} \mid \inprod{x}{v} = g(x)\}$.
If there was no $v \in \V^*$ such that $x \in F_v$, then $g(x) = \min_{H_v \in \H_\Y} \inprod{v}{x}$.
As these halfspaces are vertical, we have $g(x) = -\infty$, which does not support $G$ at $(x, g(x))$ since $x \in \reals_+^\Y$, yielding a contradiction.
\jessie{Don't like this. Slash not true.  There's something implicit about all the normals being in $\R^d_-$ and $x \in \reals^d_+$.  Haven't proven the first claim}
%We claim $\cup_{v \in \V}\pi(F_v) = \reals_+^\Y$.
%If there was a $v \in \V$ such that $\pi(F_v) \not \subseteq \reals_+^\Y$, this would imply there is some $x \not \in \reals_+^\Y$ such that $\inprod{x}{v} = c < \infty = g(x)$, contradicting $F_v$ supporting $g$ at $x$.
%Thus, $\cup_{v \in \V} \pi(F_v) \subseteq \reals_+^\Y$.
%Now for the other direction of subset inclusion, observe that for all $x \in \reals^\Y_+$, we have $g(x) = f(x) = \min_{v \in \V}\inprod{v}{x}$, so there is a $v \in \V$ supporting $g$ at $x$, and therefore $x \in \pi(F_v)$ for some $v \in \V$, and is therefore in the union of projections.
%As we have shown both directions of set inclusion, we must have $\cup_{v \in \V}\pi(F_v) = \reals_+^\Y$.	
\end{proof}
